Rough Draft

### 2017-11-15 Article submission/roughdraft.tex
edited intro + appendix

Community-driven online question and answer forums (CQA) are becoming increasingly valuable sources of information. These platforms house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. There are forums that cover a broad range of topics, like \textit{Yahoo! Answers}, and forums focused on specific topics, like computer programming-focused \textit{Stack Overflow}. An example of the latter is iFixit's \textit{Answers} forum. The \textit{Answers} forum features questions asked by users specifically related to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices. Thus, it is important that questions receive timely answers. This paper presents a survival analysis on the time until a question receives its first answer. We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$). Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.

@@

    Community-driven online question and answer forums (CQA) are becoming widely used sources of information. These online platforms allow for anyone to ask or answer a question, regardless of their background or expertise level. One popular CQA is Yahoo! Answers, featuring questions of all topics and expertise levels. On the other hand of the spectrum is Stack Overflow, the CQA that features strictly computer programming question and answers. Forums like these receive around 40 million visits every month.

    The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit helps thousands of people repair their broken devices everyday, by providing over 30,000 free online repair guides and by selling the specialized tools and parts needed for such repairs. The mission of iFixit is to enable people to extend the lifetime of their own devices, effectively saving them money and reducing electronic waste.

    As not all possible repairs are covered in the published repair guides, and users may have questions related to those guides, iFixit's \textit{Answers} forum is another important resource. This platform features questions related to over 9,000 devices with over 100,000 solutions. Questions range from broken devices like jammed zippers to shattered iPhone screens. As many rely on this forum for help with repairs, it is important that users receive timely answers. Fast response times will enhance user engagement and generate more web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of answer times can reveal factors that affect how quickly questions are answered, which can lead to suggestions for how users can ask better questions to minimize answer times, and for how the forum design can be improved.

@@

(Discuss importance of findings, not repeat them. A combined results + discussion section is often appropriate) 
The data we analyzed for this model presented some limitations. Currently, askers have a considerable amount of freedom in the way they ask a question. As a result many have incorrectly specified various input fields when asking their question. For example, a question about a faulty Android tablet screen included as a tag ``someone sat on it :(''. Generally, tags are not more than a couple key words that describe the topic of the question. Many askers on this forum included lengthy and somewhat ambiguous tags in their question. Another issue was the incorrect naming of the device the asker's question was about. A user asking a question about their Turtle Beach Ear Force X device included as the name of their device "Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One". The inconsistencies in this data made it somewhat difficult to analyze, and possibly contributes to the model's low predictive accuracy.

@@

The data contained the original category variable as defined by iFixit. This category variable contained NAs (include how many), a result of the asker creating a question for a device not already on the website's data base. Questions that made the device clear were categorized accordingly. However there were a number of questions that did not explicitly declare the device their question pertained too. These questions were categorized as ``Other''. All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category. After pulling out iPhones from the original ``Phones'' category, the remaining phones were categorized as ``AndroidOther Phone''. Appliance and Household categories of the original variable were merged into ``Home''. ``Car and Truck'' were added to the ``Vehicle''. Lastly, any category that contained less than 2\% of the questions were categorized as ``Other''. All other categories remained the same as the original category. The final categories in the new categorization variable were Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.

>>>>

Community-driven online question and answer forums (CQA) house an expansive amount of crowd-sourced knowledge in the form of thousands of questions and answers posted everyday. Forums can cover a broad range of topics, like \textit{Yahoo! Answers}, or can be focused on a specific topic, like computer programming-focused \textit{Stack Overflow}. An example of the latter is iFixit's \textit{Answers} forum. The \textit{Answers} forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users, furthering iFixit's mission to enable individuals to repair their own devices. As such, it is important that questions receive timely answers. This paper presents a survival analysis on the time until a question receives its first answer. We developed a Cox proportional hazards model to predict the failure probability of a question, or the probability that a question receives an answer before a certain time. Though we identified signifcant predictors, the predictive accuracy was low ($R^2 = 0.15$). Our findings indicate that the most important predictors were the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.56, 95\% CI = (2.31, 2.82))) and factors related to the question's title (e.g., whether or not it was phrased as a question (HR = 1.31, 95\% CI = (1.22, 1.41))). Future studies could investigate if the factors identified as signifcant in our study can be generalized to other CQAs.

@@

    Community-driven online question and answer forums (CQA) are becoming widely used sources of information. These online platforms allow for anyone to ask or answer a question, regardless of their background or expertise level. Forums can receive around 40 million visits every month.

    The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit's mission is to enable people to repair their broken devices, effectively saving them money and reducing electronic waste. The company provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs.

    As not all possible repairs are covered in the published repair guides, and users may have questions related to those guides, iFixit's \textit{Answers} forum is another important resource. This platform features questions pertaining to over 9,000 devices with over 100,000 solutions. Questions range from broken devices like jammed zippers to shattered iPhone screens. As many rely on this forum for help with repairs, it is important that users receive timely answers. Fast response times will enhance user engagement and generate more web traffic, which is valuable to the reputation and longevity of the \textit{Answers} forum. Analysis of answer times can reveal factors that affect how quickly questions are answered, which can lead to suggestions for how users can ask better questions to minimize answer times, and for how the forum design can be improved.

@@

(Discuss importance of findings, not repeat them. A combined results + discussion section is often appropriate) 
The data we analyzed for this model presented some limitations. Currently, askers have a considerable amount of freedom in the way they ask a question. As a result many incorrectly specify various input fields. For example, a question about a faulty Android tablet screen included as a tag ``someone sat on it :(''. Generally, tags are not more than a couple key words that describe the topic of the question. Many users on this forum included lengthy and somewhat ambiguous tags in their question. Another issue was the incorrect naming of the device the user's question was about. A user asking a question about their Turtle Beach Ear Force X device included as the name of their device "Turtle Beach Ear Force Xmy grandson chewed through the wire while we was playing it's brand-new is there anyway I can have it fixedO One". The inconsistencies in this data made it somewhat difficult to analyze, and possibly contributed to the model's low predictive accuracy.

@@

The original device categorization variable, as defined by iFixit, included: Apparel, Appliance, Camera, Car and Truck, Computer Hardware, Electronics, Game Console, Household, Mac, Media Player, PC, Phone, Skills, Tablet, Vehicle. This variable also contained a considerable amount of NAs (1954, or 25.2\% of all questions). NAs are a result of users asking questions for devices not already in the website's database, or from the user incorrectly defining the device.

This category variable contained NAs (include how many), a result of the asker creating a question for a device not already on the website's data base. Questions that made the device clear were categorized accordingly. However there were a number of questions that did not explicitly declare the device their question pertained too. These questions were categorized as ``Other''. All Apple products (e.g., iPhones, iMacs, Apple watches) were given their own category. After pulling out iPhones from the original ``Phones'' category, the remaining phones were categorized as ``AndroidOther Phone''. Appliance and Household categories of the original variable were merged into ``Home''. ``Car and Truck'' were added to the ``Vehicle''. Lastly, any category that contained less than 2\% of the questions were categorized as ``Other''. All other categories remained the same as the original category. The final categories in the new categorization variable were Apple Product, Android/Other Phone, PC, Tablet, Electronics, Camera, Vehicle, Game Console, Home, and Other.
